\addcontentsline{toc}{chapter}{FOREWORD}
\pagestyle{fancy}
\begin{spacing}{1.25}
\begin{center}
\large\textbf{FOREWORD}\\ 
\end{center}
\vspace{0.5cm}
    \par
	Praises be unto God for only because of His guidance the author is able to finish this thesis.
    \par
	The thesis entitled "DEEP REINFORCEMENT LEARNING FOR GAMES USING ADAM-DQL (DEEP Q-LEARNING)" is meant to fulfill a part of academic requirements to obtain Sarjana Sains and Sarjana Komputer Universitas Pelita Harapan, Tangerang.
    \par
	There are a lot of people who have given help and support so that finishing this thesis is possible, and in this chance, the author wants to express his gratitude to every person who has helped him in the completion of this thesis.

	\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
		\item Mr. Eric Jobiliong, Ph.D., as Dean of Faculty of Science and Technology.
		\item Mrs. Sunie Rahardja, M.S.CE, as Acting Vice Dean of Faculty of Science and Technology.
		\item Mr Laurence, M.T, as Finance \& Student Affairs director of Faculty of Science and Technology.
		\item Dr. Helena Margaretha, M.Sc., the thesis advisor, who has given many insights which have helped the author to develop as a student.
		\item Dr. Ir. Samuel Lukas, M.Tech, the thesis advisor, who has given a lot of suggestions and helped the author countless times in order to complete the thesis.
		\item Mrs. Dina Stefani Lukas, S.Si., S.Inf., M.T.I., the thesis advisor, who has given a lot of guidance to the author.
		\item Mr. Kie Van Ivanky Saputra, Ph.D., the Head of Mathematics Department of Universitas Pelita Harapan, as well as the academic advisor, who has taught the author a lot of things.
		\item Lecturers and staffs in Mathematics and Informatics Department who have shared their knowledge to the author during the four years of study.
		\item Father, mother and sister who have prayed and given a lot of support.
		\item Madeleine Jose Josodipuro, who have given author a lot of help during the four years of study.
		\item The author's friends and classmates, who have spent pleasant times with the author.
		\item All other people who have helped the author either directly or indirectly in the completion of the thesis.
	\end{enumerate}

	Hopefully, this thesis is useful for every one who reads it.

\begin{flushright}
Tangerang,28 May 2018 \\ \vspace{1.25cm}
(Andrew Mahisa Halim)\\
\end{flushright}

\end{spacing}